Code Publishing Tutorial

### 2024-11-27 index.qmd
Fix link

In particular, we will assume you have installed [Git](https://git-scm.com/download/), [R](https://cloud.r-project.org/), [RStudio](https://posit.co/download/rstudio-desktop/), and [Quarto](https://quarto.org/docs/download/). Windows users may additionally need [RTools](https://cloud.r-project.org/bin/windows/Rtools/).

>>>>

In particular, we will assume you have installed [Git](https://git-scm.com/downloads), [R](https://cloud.r-project.org/), [RStudio](https://posit.co/download/rstudio-desktop/), and [Quarto](https://quarto.org/docs/download/). Windows users may additionally need [RTools](https://cloud.r-project.org/bin/windows/Rtools/).
